### 2020-04-16 Thesis-Chapter2-Background.tex
Work on proposed US laws

@@

>>>>

    % TODO: working here
The \ac{clipperchip} was a voluntary initiative from the White House with the goal of ``providing the public
with strong cryptographic tools without sacrificing the ability of law enforcement and intelligence agencies to access
unencrypted versions of those communications'' \cite{thompson_2015}. Citing the foundational role of cryptography in
security--and the potential of human rights abuses for compromised privacy--industry and prominent technical leaders
reacted negatively to the initiative \cite{kehl_right_2015} \cite{zimmermann_1996}. When security researcher Matt Blaze
discovered flaws that allowed users to subvert the \ac{clipperchip} mechanisms \cite{blaze_protocol_1994}, the proposal
died.

@@

    \law{1999}{Cyberspace Electronic Security Act}{administration_CESA_1999}{

% Bill by the White House

    \law{1999}{Enhancement of Privacy and Public Safety in Cyberspace Act}{leahy_s3083_2000}{

% Bill _on behalf of_ the White House; watered down CESA, mostly CFAA updates
